Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-02-23 manuscript/HIAs.qmd
rowwise

library(tidyverse)
library(knitr)
library(sf)
library(tmap)
library(stars)
library(terra)
library(tidyterra)
library(ggtext)
library(cowplot)
library(units)
library(rnaturalearth)
library(rnaturalearthdata)

@@

```{r forets plot}
# Forest plot
# https://stackoverflow.com/questions/58657802/forest-plot-with-subgroups-in-ggplot2
```

>>>>

library(tidyverse)
library(knitr)
library(sf)
library(tmap)
libarary(tmaptools)
library(stars)
library(terra)
library(tidyterra)
library(ggtext)
library(cowplot)
library(units)
library(rnaturalearth)
library(rnaturalearthdata)

@@

```{r forets plot}
# Forest plot
# https://stackoverflow.com/questions/58657802/forest-plot-with-subgroups-in-ggplot2
# 
# #define colours for dots and bars
dotCOLS = c("grey90","grey70", "grey50", "grey40")
barCOLS <- tmaptools::get_brewer_pal("Set1", n = 4)

stats_tbl |>
  mutate(
    indicator = case_when(
      indicator == "i_ADSV" ~ "ADSV",
      indicator == "i_alien" ~ "Alien species",
      indicator == "i_ditch" ~ "Trenching"
    )
  ) |>
  rowwise() |>
  mutate(
    low = quantile(rnorm(200, mean, sd), probs = 0.025),
    high = quantile(rnorm(200, mean, sd), probs = 0.975),
    high = ifelse(high > 1, 1, high)
  ) |>
  ggplot(aes(x=infrastructureIndex, 
             y=mean, 
             ymin=low,
             ymax=high,
             col=factor(infrastructureIndex),
             fill=factor(infrastructureIndex))) + 
  geom_linerange(
    size=10,
  geom_point(
    size=3, 
    shape=21, 
    colour="white", 
    stroke = 0.5,
    ) +
  geom_text(
    aes(y = low, label = n),
    nudge_y = -0.1,
    show.legend = F
  ) +
  scale_fill_manual(values=dotCOLS)+
  scale_color_manual(values=barCOLS)+
  scale_x_discrete(name="") +
  scale_y_continuous(name="Indicator values", limits = c(-0.1, 1)) +
  coord_flip() +
  theme_bw() +
  labs(fill = "HIA",
       col = "HIA") +
  facet_grid(indicator ~ Municipality)
```

```{r}
# Next I need to 
#  - copy the weighted means and SDs over to the ecosystem delineation map polygons 
#  - show intermittent resulting map with ggmagnify
#  - sample from these distributions (ignore missing HIAs)
```

```{r}
